### 2016-02-13 mcmc.tex
Fix typo (?)

There is no general, problem-independent solution for either of these
problems.
Indeed, there are many different strategies that work well or badly
for different functions $f(\pars)$.
In this \sectionname, we will try to guide the reader towards methods
that might help in different circumstances.
We will not give a full description of all the \MCMC\ algorithms out
there, but just provide some field notes and pointers to references.
New \MCMC\ methods are being developed all the time, so a reader with a
serious problem would do well to consult with the applied-mathematics
or statistics literature.\note{Your best interface to these
  literatures is often a colleague in another department, like applied
  mathematics, statistics, or computer science.  Break down those
  walls!}
The different methods to which we refer here are (in general) very
different in their difficulty of implementation.
We won't help with that either, except to say that there are more and
more open-source or distributed packages every year.
We will try to name some current implementations in the notes, but any
list compiled today will be incomplete tomorrow.\note{One check-point
  in this literature is the compliation volume by
  \citet{mcmchandbook}, but much has been developed and changed even
  since that was written.}
The spaces of \MCMC\ methods and \MCMC\ method implementations are both
growing rapidly, in part because \MCMC\ has become such a core
technology in the empirical sciences.

>>>>

There is no general, problem-independent solution for either of these
problems.
Indeed, there are many different strategies that work well or badly
for different functions $f(\pars)$.
In this \sectionname, we will try to guide the reader towards methods
that might help in different circumstances.
We will not give a full description of all the \MCMC\ algorithms out
there, but just provide some field notes and pointers to references.
New \MCMC\ methods are being developed all the time, so a reader with a
serious problem would do well to consult with the applied-mathematics
or statistics literature.\note{Your best interface to these
  literatures is often a colleague in another department, like applied
  mathematics, statistics, or computer science.  Break down those
  walls!}
The different methods to which we refer here are (in general) very
different in their difficulty of implementation.
We won't help with that either, except to say that there are more and
more open-source or distributed packages every year.
We will try to name some current implementations in the notes, but any
list compiled today will be incomplete tomorrow.\note{One check-point
  in this literature is the compilation volume by
  \citet{mcmchandbook}, but much has been developed and changed even
  since that was written.}
The spaces of \MCMC\ methods and \MCMC\ method implementations are both
growing rapidly, in part because \MCMC\ has become such a core
technology in the empirical sciences.
